---
title: "Weight of Fish"
author: "Marcia Sanchez"
date: "`r Sys.Date()`"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
require(leaps)
```



# Predicting Fish Weight
```{r}
fish <- read.csv(file = "Fish.csv")
```

```{r eval=TRUE}
 
fish <- fish %>%
mutate(across(where(is.character), as.factor))
levels(fish$Species)
Bream <- filter(fish, Species == "Bream")
Bream <- select(Bream, -Species) 
Parkki <- filter(fish, Species == "Parkki")
Parkki <- select(Parkki, -Species) 
Perch <- filter(fish, Species == "Perch")
Perch <- select(Perch, -Species) 
Pike <- filter(fish, Species == "Pike")
Pike <- select(Pike, -Species) 
Roach <- filter(fish, Species == "Roach")
Roach <- select(Roach, -Species) 
Smelt <- filter(fish, Species == "Smelt")
Smelt <- select(Smelt, -Species) 
Whitefish <- filter(fish, Species == "Whitefish")
Whitefish <- select(Whitefish, -Species) 
```

# For each of the three species of fish listed below, determine the best regression model and also the best 2 element regression model. Use the BestSubset Regression helper file.


## Perch

### Best Models

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="topright",main="Adjusted R^2")
```

### Best Two regressor model

Best two regression models are height and width.

```{r}
Perchmodel <-lm(Weight~Height+Width, data=Perch)
summary.lm(Perchmodel)
```

The adjusted r_square is 0.94 and the residual standard error is 85.17. The p Value is 2.2e-16.  



## Pike

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottomright",main="Adjusted R^2")
```


The best element model is L1 and L3, and the best regression model is all of them.


### Best Models

```{r}
Pikebest <-lm(Weight~.,data=Pike)
summary.lm(Pikebest)
``` 



The adjusted r -square is 0.9794  and the residual standard Error is 70.86. the p value is 8.679e. This is the best model.


### Best Two regressor model

```{r}
Piketwo <-lm(Weight~Length1+Length3, data=Pike)
summary.lm(Piketwo)
```

The residual standard error is 92.56
The Adjusted r square is 0.9649
The P value is 2.57e-11
The smallest P value is the best result.


## Roach

```{r}
library(leaps)
regsubsets.out <-
    regsubsets(Weight ~ .,
               data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
library(car)
subsets(regsubsets.out,statistic="adjr2",legend="bottom",main="Adjusted R^2")
```

The best regression model is width. The second best regression is Length3 and width.


### Best Models

```{r}
Roachbest <-lm(Weight~.,data=Roach)
summary.lm(Roachbest)
``` 

This code is creating a linear regression model to understand how the "Weight" of roach fish is related to other variables in the dataset "Roach." Then, it generates a summary of the model to help us interpret the results and understand how well the model explains the relationship between the variables.


### Best Two regressor model

```{r}
Roachtwo <-lm(Weight~Length1+Length3, data=Roach)
summary.lm(Roachtwo)
```

This code is creating a linear regression model to understand how the "Weight" of roach fish is related to their "Length1" and "Length3." Then, it generates a summary of the model to help us interpret the results and understand how well the lengths of the roach fish explain their weight.

## Final Summary Statements

Today I learned to create plots and compared the three fishes type. I also learned to create a linear regression model and how each element is related to the length, width and height. Then to interpret the results.
